method

### 2022-02-28 06_Paper/ER-ED/method.Rmd
Update method.Rmd
added reference for EMG

Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence [@Bradley2000].
Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of @Fridlund1986.
The ground electrode will be placed over the left *Mastoid*.
Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
Impedance level will be kept below 10 $k\Omega$. 
Data will be sampled at 1000 Hz, filtered, rectified and integrated. 
A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset [@Bradley2000]. 
Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.

>>>>

Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence [@Bradley2000], similar to previous work by our group [@Gärtner, Jawinski, Strobel, 2021].
<!-- da wir das ja sogar schon gemacht haben, fände ich es cool die Studie zu erwähnen. :-) Zeigt ja auch, dass wir keine Neulinge auf dem Gebiet sind. Referenz muss glaub noch in Bib eingefügt werden! --> 
Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of @Fridlund1986.
The ground electrode will be placed over the left *Mastoid*.
Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
Impedance level will be kept below 10 $k\Omega$. 
Data will be sampled at 1000 Hz, filtered, rectified and integrated. 
A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset [@Bradley2000]. 
Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
